---
title: "General Education Offerings"
author: "Dr. Clifton Franklund"
date: "4/22/2020"
output:
  html_document: default
  word_document: default
  pdf_document: default
always_allow_html: yes
---

```{r libraries, echo=FALSE, message=FALSE, error=FALSE, warning=FALSE, results=FALSE}
######################################################################
## THIS SCRIPT READS THE RAW DATAFILE AND GENERATES SUMMARY REPORTS ##
######################################################################

## READ IN THE LIBRARIES THAT WE NEED
library(tidyverse)
library(readxl)
library(writexl)
library(knitr)
library(pander)
library(formattable)
```


```{r pander, echo=FALSE, message=FALSE, error=FALSE, warning=FALSE}
# set pander table-layout options
library(pander)
panderOptions('table.alignment.default', function(df)
    ifelse(sapply(df, is.numeric), 'right', 'left'))
panderOptions('table.split.table', Inf)
panderOptions('big.mark', ",")
panderOptions('keep.trailing.zeros', TRUE)
```

```{r summarize, echo=FALSE, error=FALSE, warning=FALSE, message=FALSE}
## LOAD CLEAN DATA
cleanData <- read_csv("../output/data/cleanData.csv")

## SUMMARIZE DATA BY COMPETENCY
#--> COLL
collData <- read_csv("../output/data/collData.csv")
collRecords <- length(collData$Name)
collInstructors <- length(unique(collData$Instructor))
collCourses <- length(unique(collData$Course))
collSections <- length(unique(collData$CRN))
collStudents <- length(unique(collData$Name))

#---> COMS
comsData <- read_csv("../output/data/comsData.csv")
comsRecords <- length(comsData$Name)
comsInstructors <- length(unique(comsData$Instructor))
comsCourses <- length(unique(comsData$Course))
comsSections <- length(unique(comsData$CRN))
comsStudents <- length(unique(comsData$Name))

#---> COMW
comwData <- read_csv("../output/data/comwData.csv")
comwRecords <- length(comwData$Name)
comwInstructors <- length(unique(comwData$Instructor))
comwCourses <- length(unique(comwData$Course))
comwSections <- length(unique(comwData$CRN))
comwStudents <- length(unique(comwData$Name))

#---> CULT
cultData <- read_csv("../output/data/cultData.csv")
cultRecords <- length(cultData$Name)
cultInstructors <- length(unique(cultData$Instructor))
cultCourses <- length(unique(cultData$Course))
cultSections <- length(unique(cultData$CRN))
cultStudents <- length(unique(cultData$Name))

#---> DIVG
divgData <- read_csv("../output/data/divgData.csv")
divgRecords <- length(divgData$Name)
divgInstructors <- length(unique(divgData$Instructor))
divgCourses <- length(unique(divgData$Course))
divgSections <- length(unique(divgData$CRN))
divgStudents <- length(unique(divgData$Name))

#---> DIVU
divuData <- read_csv("../output/data/divuData.csv")
divuRecords <- length(divuData$Name)
divuInstructors <- length(unique(divuData$Instructor))
divuCourses <- length(unique(divuData$Course))
divuSections <- length(unique(divuData$CRN))
divuStudents <- length(unique(divuData$Name))

#---> NSCI
nsciData <- read_csv("../output/data/nsciData.csv")
nsciRecords <- length(nsciData$Name)
nsciInstructors <- length(unique(nsciData$Instructor))
nsciCourses <- length(unique(nsciData$Course))
nsciSections <- length(unique(nsciData$CRN))
nsciStudents <- length(unique(nsciData$Name))

#---> PROB
probData <- read_csv("../output/data/probData.csv")
probRecords <- length(probData$Name)
probInstructors <- length(unique(probData$Instructor))
probCourses <- length(unique(probData$Course))
probSections <- length(unique(probData$CRN))
probStudents <- length(unique(probData$Name))

#---> QUAN
quanData <- read_csv("../output/data/quanData.csv")
quanRecords <- length(quanData$Name)
quanInstructors <- length(unique(quanData$Instructor))
quanCourses <- length(unique(quanData$Course))
quanSections <- length(unique(quanData$CRN))
quanStudents <- length(unique(quanData$Name))

#---> SSOC
ssocData <- read_csv("../output/data/ssocData.csv")
ssocRecords <- length(ssocData$Name)
ssocInstructors <- length(unique(ssocData$Instructor))
ssocCourses <- length(unique(ssocData$Course))
ssocSections <- length(unique(ssocData$CRN))
ssocStudents <- length(unique(ssocData$Name))

## MAKE A MASTER TIBBLE
#--> Create vectors of data
Competency <- c("Collaboration","Communication - Oral","Communication - Written","Culture","Diversity - Global","Diversity - Race, Ethnicity, Gender","Natural Sciences","Problem Solving","Quantitative Literacy","Self and Society")
Courses <- c(collCourses,comsCourses,comwCourses,cultCourses,divgCourses,divuCourses,nsciCourses,probCourses,quanCourses,ssocCourses)
Sections <- c(collSections,comsSections,comwSections,cultSections,divgSections,divuSections,nsciSections,probSections,quanSections,ssocSections)
Instructors <- c(collInstructors,comsInstructors,comwInstructors,cultInstructors,divgInstructors,divuInstructors,nsciInstructors,probInstructors,quanInstructors,ssocInstructors)
Students <- c(collStudents,comsStudents,comwStudents,cultStudents,divgStudents,divuStudents,nsciStudents,probStudents,quanStudents,ssocStudents)
Records <- c(collRecords,comsRecords,comwRecords,cultRecords,divgRecords,divuRecords,nsciRecords,probRecords,quanRecords,ssocRecords)
#--> Assemble into a tibble
summaryTable <- tibble(Competency=Competency,Courses=Courses,Sections=Sections,Instructors=Instructors,Students=Students,Records=Records)
summaryTable <- summaryTable %>% 
	add_row(Competency="Totals",Courses=sum(Courses),Sections=sum(Sections),Instructors=sum(Instructors),Students=sum(Students),Records=sum(Records))

## Record the tibble as a csv file in our temporary data file
write_csv(summaryTable, "../output/data/reportTable.csv")
```

The General Education instructional dataset for the `r ssocData$Semester[1]` semester of `r ssocData$Year[1]` included a total of `r comma(summaryTable[11,6],format="d")` student records. This represented `r comma(length(unique(cleanData$Course)),format="d")` unique courses that were delivered in `r comma(length(unique(cleanData$CRN)),format="d")` total sections. These classes were taught by `r comma(length(unique(cleanData$Instructor)),format="d")` unique instructors. Some students were enrolled in more than one General Education course for a particular competency and some instructors taught courses with more than one General Education designation. Because of this, there are more total values (when adding up all the competencies) than the original dataset actually contained. Here is a brief breakdown of the records for this semester.

```{r table, echo=FALSE}
## PUT THE TIBBLE IN THE DOCUMENT AS A TABLE
pander(summaryTable)
```
