---
title: "General Education Offerings, Spring 2020"
author: "Dr. Clifton Franklund"
date: "4/22/2020"
output:
  html_document: default
  word_document: default
  pdf_document: default
always_allow_html: yes
---

```{r libraries, echo=FALSE, message=FALSE, error=FALSE, warning=FALSE, results=FALSE}
## READ IN THE LIBRARIES THAT WE NEED
library(tidyverse)
library(readxl)
library(writexl)
library(knitr)
library(pander)
library(formattable)
```

```{r variables, echo=FALSE}
## SET THE VARIABLES FOR THE ASSESSMENT PERIOD HERE
theYear <- "2020"
theSemester <- "Spring"
collVar <- "COL1"
comsVar <- "COMS1"
comwVar <- "COMW1"
cultVar <- "CUL1"
divgVar <- "DIVG1"
divuVar <- "DIVU1"
nsciVar <- "SCI1"
probVar <- "PRB1"
quanVar <- "QNT1"
ssocVar <- "SOC1"
```

```{r pander, echo=FALSE, message=FALSE, error=FALSE, warning=FALSE}
# set pander table-layout options
library(pander)
panderOptions('table.alignment.default', function(df)
    ifelse(sapply(df, is.numeric), 'right', 'left'))
panderOptions('table.split.table', Inf)
panderOptions('big.mark', ",")
panderOptions('keep.trailing.zeros', TRUE)
```

```{r data, echo=FALSE, message=FALSE, error=FALSE, warning=FALSE}
## READ IN THE DATA AND FORMAT IT
myData <- read_xlsx("../rawdata/202001-GenEd-Data.xlsx")

#--> Rename the variables
myData <- myData %>%  rename(Term=TERM,
					CRN=CRN,
					College=COURSE_COLL_CODE,
					Prefix=SUBJ,
					Number=CRSE_NUMB,
					Section=SECTION,
					ID=ID,
					Name=STU_NAME,
					Instructor=INSTR_NAME)

#--> Recode the colleges
myData[myData$College=="AS","College"] <- "CAS"
myData[myData$College=="BU","College"] <- "COB"
myData[myData$College=="ED","College"] <- "COEHS"
myData[myData$College=="TE","College"] <- "CET"
myData[myData$College=="HP","College"] <- "CHP"
myData[myData$College=="UN","College"] <- "UNIV"

#--> Add new variables
myData$Course <- paste0(myData$Prefix,myData$Number)
myData <- myData %>% separate(Instructor,c("Instructor.Last","Instructor.First"), ",", remove=FALSE)
myData$Full.Name <- paste(myData$Instructor.First,myData$Instructor.Last)
```

```{r summarize, echo=FALSE, error=FALSE, warning=FALSE}
## SPLIT OUT DATA BY COMPETENCY
#--> COLL
collData <- myData %>% 
	filter(COLL == 1)
collRecords <- length(collData$Name)
collInstructors <- length(unique(collData$Instructor))
collCourses <- length(unique(collData$Course))
collSections <- length(unique(collData$CRN))
collStudents <- length(unique(collData$Name))

#---> COMS
comsData <- myData %>% 
	filter(COMS == 1)
comsRecords <- length(comsData$Name)
comsInstructors <- length(unique(comsData$Instructor))
comsCourses <- length(unique(comsData$Course))
comsSections <- length(unique(comsData$CRN))
comsStudents <- length(unique(comsData$Name))

#---> COMW
comwData <- myData %>% 
	filter(COMW == 1)
comwRecords <- length(comwData$Name)
comwInstructors <- length(unique(comwData$Instructor))
comwCourses <- length(unique(comwData$Course))
comwSections <- length(unique(comwData$CRN))
comwStudents <- length(unique(comwData$Name))

#---> CULT
cultData <- myData %>% 
	filter(!is.na(ACTC) | !is.na(CATC) | !is.na(CLTR))
cultRecords <- length(cultData$Name)
cultInstructors <- length(unique(cultData$Instructor))
cultCourses <- length(unique(cultData$Course))
cultSections <- length(unique(cultData$CRN))
cultStudents <- length(unique(cultData$Name))

#---> DIVG
divgData <- myData %>% 
	filter(DIVG == 1)
divgRecords <- length(divgData$Name)
divgInstructors <- length(unique(divgData$Instructor))
divgCourses <- length(unique(divgData$Course))
divgSections <- length(unique(divgData$CRN))
divgStudents <- length(unique(divgData$Name))

#---> DIVU
divuData <- myData %>% 
	filter(DIVU == 1)
divuRecords <- length(divuData$Name)
divuInstructors <- length(unique(divuData$Instructor))
divuCourses <- length(unique(divuData$Course))
divuSections <- length(unique(divuData$CRN))
divuStudents <- length(unique(divuData$Name))

#---> NSCI
nsciData <- myData %>% 
	filter(NSCL == 1 | NSCI == 1)
nsciRecords <- length(nsciData$Name)
nsciInstructors <- length(unique(nsciData$Instructor))
nsciCourses <- length(unique(nsciData$Course))
nsciSections <- length(unique(nsciData$CRN))
nsciStudents <- length(unique(nsciData$Name))

#---> PROB
probData <- myData %>% 
	filter(PROB == 1)
probRecords <- length(probData$Name)
probInstructors <- length(unique(probData$Instructor))
probCourses <- length(unique(probData$Course))
probSections <- length(unique(probData$CRN))
probStudents <- length(unique(probData$Name))

#---> QUAN
quanData <- myData %>% 
	filter(QUAL == 1)
quanRecords <- length(quanData$Name)
quanInstructors <- length(unique(quanData$Instructor))
quanCourses <- length(unique(quanData$Course))
quanSections <- length(unique(quanData$CRN))
quanStudents <- length(unique(quanData$Name))

#---> SSOC
ssocData <- myData %>% 
	filter(SSOC == 1 | SSOF == 1)
ssocRecords <- length(ssocData$Name)
ssocInstructors <- length(unique(ssocData$Instructor))
ssocCourses <- length(unique(ssocData$Course))
ssocSections <- length(unique(ssocData$CRN))
ssocStudents <- length(unique(ssocData$Name))

## MAKE A MASTER TIBBLE
#--> Create vectors of data
Competency <- c("Collaboration","Communication - Oral","Communication - Written","Culture","Diversity - Global","Diversity - Race, Ethnicity, Gender","Natural Sciences","Problem Solving","Quantitative Literacy","Self and Society")
Courses <- c(collCourses,comsCourses,comwCourses,cultCourses,divgCourses,divuCourses,nsciCourses,probCourses,quanCourses,ssocCourses)
Sections <- c(collSections,comsSections,comwSections,cultSections,divgSections,divuSections,nsciSections,probSections,quanSections,ssocSections)
Instructors <- c(collInstructors,comsInstructors,comwInstructors,cultInstructors,divgInstructors,divuInstructors,nsciInstructors,probInstructors,quanInstructors,ssocInstructors)
Students <- c(collStudents,comsStudents,comwStudents,cultStudents,divgStudents,divuStudents,nsciStudents,probStudents,quanStudents,ssocStudents)
Records <- c(collRecords,comsRecords,comwRecords,cultRecords,divgRecords,divuRecords,nsciRecords,probRecords,quanRecords,ssocRecords)
#--> Assemble into a tibble
summaryTable <- tibble(Competency=Competency,Courses=Courses,Sections=Sections,Instructors=Instructors,Students=Students,Records=Records)
summaryTable <- summaryTable %>% 
	add_row(Competency="Totals",Courses=sum(Courses),Sections=sum(Sections),Instructors=sum(Instructors),Students=sum(Students),Records=sum(Records))
```

The General Education instructional dataset for the `r theSemester` semester of `r theYear` included a total of `r comma(length(myData$CRN),format="d")` student records. This represented `r comma(length(unique(myData$Course)),format="d")` courses which were delivered in `r comma(length(unique(myData$CRN)),format="d")` total sections. These classes were taught by `r comma(length(unique(myData$Instructor)),format="d")` different instructors. Some students were enrolled in more than one General Education course for a particular competency. Therefore, there were fewer unique students (`r comma(length(unique(myData$Name)),format="d")`) than records. In addition, some courses count for more than one of the General Education core competencies (double- or triple-dippers). Because of this, there are more total values (when adding up all the competencies) than the original dataset actually contained. Here is a brief breakdown of the records for this semester.

```{r table, echo=FALSE}
## PUT THE TIBBLE IN THE DOCUMENT AS A TABLE
pander(summaryTable)
```
